
    \bgroup
    \def\arraystretch{1.5}
    \setlength\arrayrulewidth{1.2pt}
    \color{textgray}
    \begin{xltabular}{\textwidth}{|X|M{3cm}|}

\caption*{} \label{tab:Requirements - Non-Functional} \\

\arrayrulecolor{linegray}\hline \rowcolor{lightgray} \multicolumn{1}{|c|}{\color{default}\textbf{User Story}} & \multicolumn{1}{c|}{\color{default}\textbf{Scope}}\\ \hline

 \endfirsthead 
 \multicolumn{2}{c}%
{\tablename\ \thetable{} -- continued from previous page} \\ \hline \multicolumn{1}{|c|}{\textbf{User Story}} & \multicolumn{1}{c|}{\textbf{Scope}}\\ \hline 
\endhead \hline 
\multicolumn{2}{|r|}{{Continued on next page}} \\ \hline 
\endfoot

\hline 
 \endlastfoot 
As a user I want to be able to rotate the plane by providing euler angles. & \tcbox[colframe=TAGgreen, colback=TAGgreen]{\textbf{\footnotesize MUST HAVE}} \\ \hline 
  As a user I want to be able to see the current angle and distance between a selected threat and the plane. & \tcbox[colframe=TAGgreen, colback=TAGgreen]{\textbf{\footnotesize MUST HAVE}} \\ \hline 
  As a user I want to be abler to freely translate the plane in space by providing a translation vector in cartesian coordinates. & \tcbox[colframe=TAGgreen, colback=TAGgreen]{\textbf{\footnotesize MUST HAVE}} \\ \hline 
  As a user I want to freely add and remove individual threats to the scene. & \tcbox[colframe=TAGgreen, colback=TAGgreen]{\textbf{\footnotesize MUST HAVE}} \\ \hline 
  As a user I want to see a 3D representation of the plane and threats. & \tcbox[colframe=TAGgreen, colback=TAGgreen]{\textbf{\footnotesize MUST HAVE}} \\ \hline 
  As a user I would like to see a 2D projection next to the 3D scene. Akin to the stereotypical image of a submarine radar. & \tcbox[colframe=TAGgreen, colback=TAGgreen]{\textbf{\footnotesize MUST HAVE}} \\ \hline 
  As a user I want to move threats in space by providing a translation vector. & \tcbox[colframe=TAGyellow, colback=TAGyellow]{\textbf{\footnotesize NICE TO HAVE}} \\ \hline 
  As a user I would like to enter a full transformation matrix by hand and see its effect on the plane and/or bird. & \tcbox[colframe=TAGyellow, colback=TAGyellow]{\textbf{\footnotesize NICE TO HAVE}} \\ \hline 
  As a user I would like to move the calculation center arbitrarily. & \tcbox[colframe=TAGyellow, colback=TAGyellow]{\textbf{\footnotesize NICE TO HAVE}} \\ \hline 
  As a user I would like to visually differentiate my added threats. & \tcbox[colframe=TAGyellow, colback=TAGyellow]{\textbf{\footnotesize NICE TO HAVE}} \\ \hline 
  As a user I would like to see an animation of the entered movement. & \tcbox[colframe=TAGred, colback=TAGred]{\textbf{\footnotesize NOT IN SCOPE}} \\ \hline 
  As a user I would like to use this tool on all my devices. & \tcbox[colframe=TAGred, colback=TAGred]{\textbf{\footnotesize NOT IN SCOPE}} \\ \hline 
  
\end{xltabular} 
 \egroup 
 \color{default}