
    \bgroup
    \def\arraystretch{1.5}
    \setlength\arrayrulewidth{1.2pt}
    \color{textgray}
    \begin{xltabular}{\textwidth}{|M{1.2cm}|X|X|M{3cm}|}

\caption*{} \label{tab:math_functions} \\

\arrayrulecolor{linegray}\hline \rowcolor{lightgray} \multicolumn{1}{|c|}{\color{default}\textbf{ID}} & \multicolumn{1}{c|}{\color{default}\textbf{Function/Method}} & \multicolumn{1}{c|}{\color{default}\textbf{Description}} & \multicolumn{1}{c|}{\color{default}\textbf{Coverage}}\\ \hline

 \endfirsthead 
 \multicolumn{4}{c}%
{\tablename\ \thetable{} -- continued from previous page} \\ \hline \multicolumn{1}{|c|}{\textbf{ID}} & \multicolumn{1}{c|}{\textbf{Function/Method}} & \multicolumn{1}{c|}{\textbf{Description}} & \multicolumn{1}{c|}{\textbf{Coverage}}\\ \hline 
\endhead \hline 
\multicolumn{4}{|r|}{{Continued on next page}} \\ \hline 
\endfoot

\hline 
 \endlastfoot 
\textbf{ F1 } & {\ttfamily azimuthAngle(A: Point, center?: Point): number} & Calculates the angle measure (in radians, with $-\pi \textless \theta \le \pi$ between the positive x-axis and the ray from the origin to the point {\ttfamily(x,y)} in the Cartesian plane.\newline If a center point is provided, the angle is calculated from the new center position. & \tcbox[colframe=TAGgreen, colback=TAGgreen]{\textbf{\footnotesize 100\%}} \\ \hline 
  \textbf{F02} & {\ttfamily yawPitchRoll2Matrix( \newline yaw: number,\newline pitch: number,\newline roll: number\newline): number[][]} & Returns a $3x3$ rotations matrix that represents a rotation in ZYX order in degree. \newline Yaw, Pitch and Roll are in degrees. & \tcbox[colframe=TAGgreen, colback=TAGgreen]{\textbf{\footnotesize 100\%}} \\ \hline 
  \textbf{F03} & {\ttfamily cosineDegrees(degrees: number): number } & Calculates the cosine of a number in degrees. & \tcbox[colframe=TAGgreen, colback=TAGgreen]{\textbf{\footnotesize 100\%}} \\ \hline 
  \textbf{F04} & {\ttfamily sineDegrees(degrees: number): number} & Calculates the sine of a number in degrees. & \tcbox[colframe=TAGgreen, colback=TAGgreen]{\textbf{\footnotesize 100\%}} \\ \hline 
  \textbf{F05} & {\ttfamily rad2Degrees(rad: number): number} & Converts rad to degrees. & \tcbox[colframe=TAGgreen, colback=TAGgreen]{\textbf{\footnotesize 100\%}} \\ \hline 
  \textbf{F06} & {\ttfamily crossProduct(pointA: Point, pointB: Point): Point} & Calculates the cross product between two vectors & \tcbox[colframe=TAGgreen, colback=TAGgreen]{\textbf{\footnotesize 100\%}} \\ \hline 
  \textbf{F07} & {\ttfamily vectorLength(p: Point): number} & Calculates the length of a vector & \tcbox[colframe=TAGgreen, colback=TAGgreen]{\textbf{\footnotesize 100\%}} \\ \hline 
  \textbf{F08} & {\ttfamily dotProduct(pointA: Point, pointB: Point): number} & Calculates the dot product of to vectors & \tcbox[colframe=TAGgreen, colback=TAGgreen]{\textbf{\footnotesize 100\%}} \\ \hline 
  \textbf{F09} & {\ttfamily angleBetween2Points(A: Point, B: Point): number} & The final angle between is calculated according to the dihedral angle: The dot product of the two normal vectors divided by the product of their lengths. \newline $cos(phi) = Norm(n_A * n_B) / (Norm(n_A) * Norm(n_B))$ & \tcbox[colframe=TAGgreen, colback=TAGgreen]{\textbf{\footnotesize 100\%}} \\ \hline 
  \textbf{F10} & {\ttfamily subtract2Point(pointA: Point, pointB: Point): Point} & Subtracts two vectors. & \tcbox[colframe=TAGgreen, colback=TAGgreen]{\textbf{\footnotesize 100\%}} \\ \hline 
  \textbf{F11} & {\ttfamily multiply(a: number[][], b: number[][]): number[][]} & Multiplies two matrices. & \tcbox[colframe=TAGgreen, colback=TAGgreen]{\textbf{\footnotesize 100\%}} \\ \hline 
  \textbf{F12} & {\ttfamily buildTransformationMatrix( \newline rotationMatrix: number[][], \newline  translationVector: number[] \newline ): number[][]} & Builds a transformation matrix from the rotation and translation matrix. & \tcbox[colframe=TAGgreen, colback=TAGgreen]{\textbf{\footnotesize 100\%}} \\ \hline 
  \textbf{F13} & {\ttfamily matrixTransformation( \newline transformationMatrix: number[][], \newline R: number[][] \newline ): number[][]} & Multiplies a point with a transformationsmatrix and thereby transforms it in space. & \tcbox[colframe=TAGgreen, colback=TAGgreen]{\textbf{\footnotesize 100\%}} \\ \hline 
  \textbf{M01} & {\ttfamily matrixTransform: void } & Applies all subsequent transformations to the initial plane, marble and plane coordinate system. & \tcbox[colframe=TAGgreen, colback=TAGgreen]{\textbf{\footnotesize 100\%}} \\ \hline 
  \textbf{M02} & {\ttfamily resetPlane(): Plane } & resets plane to its initial position. & \tcbox[colframe=TAGgreen, colback=TAGgreen]{\textbf{\footnotesize 100\%}} \\ \hline 
  \textbf{M03} & {\ttfamily rotatePlane(yaw: number, pitch: number, roll: number) : Plane} & Updates the rotation matrix via Euler Angles in ZYX order, rotates the plane and returns the freshly transformed plane. & \tcbox[colframe=TAGgreen, colback=TAGgreen]{\textbf{\footnotesize 100\%}} \\ \hline 
  \textbf{M04} & {\ttfamily translatePlane(x: number, y: number, z: number): Plane} & Updates the planes translation matrix, translates the plane and returns the freshly transformed plane. & \tcbox[colframe=TAGgreen, colback=TAGgreen]{\textbf{\footnotesize 100\%}} \\ \hline 
  \textbf{M05} & {\ttfamily getAngle2North(): number} & Returns the angle $\alpha$ between the planes x-Axis and the earth referential x-Axis in degrees. $\alpha\in\left[0..359\right]$ & \tcbox[colframe=TAGgreen, colback=TAGgreen]{\textbf{\footnotesize 100\%}} \\ \hline 
  \textbf{M06} & {\ttfamily getVerticalDistance2Plane(p: Point): number} & Returns the vertical hight difference between the plane and a point in space. & \tcbox[colframe=TAGgreen, colback=TAGgreen]{\textbf{\footnotesize 100\%}} \\ \hline 
  \textbf{M07} & {\ttfamily getDistance2Plane(p: Point): number} & Returns the length of the vector $\vec{MP}$ from the Marble $M$ to an arbitrary Point $P$. & \tcbox[colframe=TAGgreen, colback=TAGgreen]{\textbf{\footnotesize 100\%}} \\ \hline 
  \textbf{M08} & {\ttfamily getElevationAngle2Threat(p: Point): number} & Returns the vertical angle $\alpha$ between the Marble and an arbitrary Point. $\alpha\in\left[-179..180\right]$ & \tcbox[colframe=TAGgreen, colback=TAGgreen]{\textbf{\footnotesize 100\%}} \\ \hline 
  \textbf{M09} & {\ttfamily getAngle2Plane(location: Point): number} & Returns the horizontal/azimuth angle $\alpha$ between a point in space and the marble $\alpha\in\left[0..359\right]$ & \tcbox[colframe=TAGgreen, colback=TAGgreen]{\textbf{\footnotesize 100\%}} \\ \hline 
  \textbf{M10} & {\ttfamily getDistanceFromGround(): number} & Returns the altitude of the plane. & \tcbox[colframe=TAGgreen, colback=TAGgreen]{\textbf{\footnotesize 100\%}} \\ \hline 
  
\end{xltabular} 
 \egroup 
 \color{default}